Scikit-learn: machine learning without learning the machinery

### 2014-11-06 article.tex
how to plug a different classifier into the NLP example

>>>>

We see that the expected accuracy is about 88\%.
Experimenting with different classification models is easy:
e.g., replacing \texttt{LogisticRegression} with \texttt{svm.LinearSVC}
gives a linear support vector machine.
Changing the simple bag-of-words representation to a \textit{bigram}
(pairs of adjacent words) one is a matter of giving one additional argument
to the tf--idf vectorizer, which reads \texttt{n\_gram\_range=(2, 2)}.
(Similarly, the value \texttt{(2,3)} would extract bigrams and trigrams, etc.)
